Follow-up Samples

### 2017-01-13 submission/manuscript_outline_20161024.Rmd
added common OTUs and model data to results

***Positive Probability Prediction after Surgical Removal of Adenoma or Carcinoma***

>>>>

***Positive Probability Prediction after Surgical Removal of Adenoma or Carcinoma***
Regardless of model used there was a significant decrease in the positive probability of either the sample being lesion or an initial sample on follow up [Figure 4 & S4] (full lesion P-value = `r format(filter(all_probs_paired_wilcox, model_type =="lesion" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, reduced lesion P-value = `r format(filter(all_probs_paired_wilcox, model_type =="red_lesion" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, initial and follow up P-value = `r format(filter(all_probs_paired_wilcox, model_type =="IF" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`, and reduced initial and follow up P-value = `r format(filter(all_probs_paired_wilcox, model_type =="red_IF" & comparison == "lesion")[, "BH_correction"], scientific = TRUE, digits = 3)`).

For the full and reduced lesion model there was a significant difference in the classification for the lesion model between predicted and actual (P-value = `r format(filter(all_pred_stat_summary, samples_tested == "all" & model_type == "lesion" & info == "McnemarPValue")[, "all"], scientific = TRUE, digits = 3)` and `r format(filter(all_pred_stat_summary, samples_tested == "all" & model_type == "red_lesion" & info == "McnemarPValue")[, "all"], scientific = TRUE, digits = 3)`, respectively) but not for the initial follow up model (P-value = `r format(filter(all_pred_stat_summary, samples_tested == "all" & model_type == "IF" & info == "McnemarPValue")[, "all"], digits = 3, nsmall = 2)` and `r format(filter(all_pred_stat_summary, samples_tested == "all" & model_type == "red_IF" & info == "McnemarPValue")[, "all"], digits = 3, nsmall = 2)`).  However, the lesion model correctly kept the one individual who still had a carcinoma on follow up above the cut off point [Figure 4a & S4a] for a positive call while the initial and follow up models did not [Figure 4b & S4b].

***Common OTUs to both Lesion and Initial and Follow Up Models***
There were a total of `r length(common_vars_summary$otu)` OTUs that were common to both models.  Of these OTUs the most common taxonomic identifications were to  `r common_vars_summary['Otu000012', 'lowest_ID']`, `r common_vars_summary['Otu000005', 'lowest_ID']`, `r common_vars_summary['Otu000082', 'lowest_ID']`, and `r paste(gsub("_unclassified", "", common_vars_summary['Otu000006', 'lowest_ID']))`.
